An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-08 EconGrowth-R-Functions.Rnw
Added figure from Tverberg on tightening oil supply. Got the bibliography to work, even if it is not in the format I would like, yet.

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=TRUE,
  # ********************************************************************************************************
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

>>>>

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=FALSE,
  # ********************************************************************************************************
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

### 2013-03-08 EconGrowthSeminar.Rnw
Added figure from Tverberg on tightening oil supply. Got the bibliography to work, even if it is not in the format I would like, yet.

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

@@

\begin{frame}[fragile] %----------------------------
  \frametitle{Energy and GDP are Linked} 
%  \framesubtitle{\citet{Cleveland:1997p5055}}
  \begin{columns}[c]
    \column{2.0in}
      \includegraphics[width=2.0in]{figure_other/Figure_Cleveland_1984.pdf}
    \column{1.5in}
      \includegraphics[width=1.5in]{figure_other/Figure_Cleveland_1984_Science_Cover.pdf}
  \end{columns}
\end{frame}

\begin{frame}{Problem: Energy Cost Share is Low} %----------------------------
  Therefore, energy is considered to be economically unimportant.

  Compare cost shares of capital stock, labor, and energy.
\end{frame}

@@

\begin{frame}{The Big Questions} %----------------------------
  How account for energy in economic models?

  What happens when energy supplies become constrained?

  Historical economic development paths are energy intensive. What happens when energy is constrained and prices rise? Will developing countries be able to expand their economies?
\end{frame}

@@

% See hints at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
\begin{frame}{Bibliography} %----------------------------
\bibliographystyle{model2-names}
\bibliography{EconGrowth.bib}
\end{frame}

>>>>

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.
\usepackage{url} % To format URLs in the references section.

@@

\begin{frame}{Energy and GDP are Linked} %----------------------------
  \tiny
  \framesubtitle{\cite{Cleveland:1997p5055}}
  \normalsize
  \begin{columns}[c]
    \column{2.0in}
      \includegraphics[width=2.0in]{figure_other/Figure_Cleveland_1984.pdf}
    \column{1.5in}
      \includegraphics[width=1.5in]{figure_other/Figure_Cleveland_1984_Science_Cover.pdf}
  \end{columns}
\end{frame}

\begin{frame}{World Oil Supply is Tightening} %----------------------------
  \framesubtitle{\cite{Tverberg:2013}}
  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
\end{frame}

\begin{frame}{Energy Cost Share is Low} %----------------------------
  \begin{itemize}
    \item
      Therefore, energy is considered to be economically unimportant.
    \item
      Compare cost shares of capital stock, labor, and energy.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Observations and Questions} %----------------------------
  \begin{itemize}
    \item
      Historical economic development paths are energy intensive. 
    \item
      What happens when energy supplies are constrained and prices rise? 
    \item
      Will developing countries be able to expand their economies?
    \item
      How account for energy in economic models?
  \end{itemize}
\end{frame}

@@

% See hints at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
% \begin{frame}{Bibliography} %----------------------------
% \bibliographystyle{model2-names}
% \bibliography{EconGrowth.bib}
% \end{frame}

%-------------------------------------------------------------------

\begin{frame}
\frametitle{References}
%\bibliographystyle{amsalpha}
\bibliographystyle{model2-names}
\renewcommand{\thepage}{\arabic{page}}
\tiny
\bibliography{EconGrowth.bib}
\normalsize
\end{frame}
